Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-08 outputs/paper/paper.qmd
Update

```
```{r}
# Load necessary libraries
library(ggplot2)
library(gridExtra)

# Plotting the first line graph (Graph A)
graph_A <- ggplot(data, aes(x = year)) +
  geom_line(aes(y = brate_1519, color = "Age 15-19"), size = 1.2) +
  geom_line(aes(y = brate_2024, color = "Age 20-24"), size = 1.2) +
  geom_line(aes(y = brate_2529, color = "Age 25-29"), size = 1.2) +
  geom_line(aes(y = brate_3034, color = "Age 30-34"), size = 1.2) +
  geom_line(aes(y = brate_3539, color = "Age 35-39"), size = 1.2) +
  geom_line(aes(y = brate_4044, color = "Age 40-44"), size = 1.2) +
  scale_color_manual(values = c("Age 15-19" = "blue", "Age 20-24" = "orange", "Age 25-29" = "grey",
                                 "Age 30-34" = "yellow", "Age 35-39" = "cyan", "Age 40-44" = "green"),
                     labels = c("Age 15-19", "Age 20-24", "Age 25-29", "Age 30-34", "Age 35-39", "Age 40-44"),
                     name = "Age Group") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  geom_hline(yintercept = seq(0, 140, by = 20), color = "lightgrey") +
  scale_x_continuous(limits = c(1980, 2020), breaks = seq(1980, 2020, by = 5)) +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, by = 20)) +
  labs(x = "Year", y = "Births per 1,000 women in relevant population subgroup",
       title = "Trend in US Birth Rates by Age Group",
       caption = "Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019, and 2020.") +
  theme_classic()

# Plotting the second line graph (Graph B)
graph_B <- ggplot(data, aes(x = year)) +
  geom_line(aes(y = brate_hisp, color = "Hispanic"), size = 1.2) +
  geom_line(aes(y = brate_blacknh, color = "Black, non-Hispanic"), size = 1.2) +
  geom_line(aes(y = brate_whitenh, color = "White, non-Hispanic"), size = 1.2) +
  scale_color_manual(values = c("Hispanic" = "grey", "Black, non-Hispanic" = "orange", "White, non-Hispanic" = "blue"),
                     labels = c("Hispanic", "Black, non-Hispanic", "White, non-Hispanic"),
                     name = "Race/Ethnicity") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  geom_hline(yintercept = seq(0, 140, by = 20), color = "lightgrey") +
  scale_x_continuous(limits = c(1990, 2020), breaks = seq(1990, 2020, by = 5)) +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, by = 20)) +
  labs(x = "Year", y = "Births per 1,000 women in relevant population subgroup",
       title = "Trend in US Birth Rates by Race/Ethnicity",
       caption = "Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019, and 2020.") +
  theme_classic()

@@

```{r}
# Load necessary libraries
library(ggplot2)
library(gridExtra)

@@

# Plotting the second line graph (Graph B)
graph_B <- ggplot(data, aes(x = year)) +
  geom_line(aes(y = brate_hisp, color = "Hispanic"), size = 1.2) +
  geom_line(aes(y = brate_blacknh, color = "Black, non-Hispanic"), size = 1.2) +
  geom_line(aes(y = brate_whitenh, color = "White, non-Hispanic"), size = 1.2) +
  geom_text(aes(label = "Hispanic", x = 2020, y = brate_hisp), hjust = 0, vjust = -0.5, color = "grey", family = "Times") +
  geom_text(aes(label = "Black, non-Hispanic", x = 2020, y = brate_blacknh), hjust = 0, vjust = -0.5, color = "orange", family = "Times") +
  geom_text(aes(label = "White, non-Hispanic", x = 2020, y = brate_whitenh), hjust = 0, vjust = -0.5, color = "blue", family = "Times") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  geom_hline(yintercept = seq(0, 140, by = 20), color = "lightgrey") +
  scale_x_continuous(limits = c(1990, 2020), breaks = seq(1990, 2020, by = 5), labels = function(x) paste(x, "\n")) +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, by = 20)) +
  labs(title = "B: Race and ethnicity (ages 15-44)") +
  theme_classic()

>>>>

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-trend-brate-graph
#| fig-cap: "Trends in Birth Rates by Population Subgroup"
# Load necessary libraries
library(ggplot2)
library(gridExtra)

@@

```{r}
# Plotting the second line graph (Graph B)
graph_B <- ggplot(data, aes(x = year)) +
  geom_line(aes(y = brate_hisp, color = "Hispanic"), size = 1.2) +
  geom_line(aes(y = brate_blacknh, color = "Black, non-Hispanic"), size = 1.2) +
  geom_line(aes(y = brate_whitenh, color = "White, non-Hispanic"), size = 1.2) +
  geom_text(aes(label = "Hispanic", x = 2020, y = brate_hisp), hjust = 0, vjust = -0.5, color = "grey", family = "Times") +
  geom_text(aes(label = "Black, non-Hispanic", x = 2020, y = brate_blacknh), hjust = 0, vjust = -0.5, color = "orange", family = "Times") +
  geom_text(aes(label = "White, non-Hispanic", x = 2020, y = brate_whitenh), hjust = 0, vjust = -0.5, color = "blue", family = "Times") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  geom_hline(yintercept = seq(0, 140, by = 20), color = "lightgrey") +
  scale_x_continuous(limits = c(1990, 2020), breaks = seq(1990, 2020, by = 5), labels = function(x) paste(x, "\n")) +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, by = 20)) +
  labs(title = "B: Race and ethnicity (ages 15-44)") +
  theme_classic()
  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"))
